---
title: "time series project code"
author: "Mengze(Maisie) Tang"
date: "11/19/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#data
```{r}
#install.packages("fBasics")
#install.packages("fGarch")
#install.packages("fpp2")
#install.packages("tsensembler")

library(fBasics)
library(fGarch)
library(fpp2)
library(tsensembler)


library(data.table)
tb.rates=read.csv("tb_rates.csv",header=T)
tb <- ts(tb.rates$tb_rates, frequency=12, start=c(1975, 1))
tb_train1 <- window(tb, end = c(2017,12))
tb_test1<-window(tb, start=c(2018, 1))


#Original time series plot of data
autoplot(tb,ylab = "T-Bill rates")

#Transforming data to obtain stable variance
lambda1<-BoxCox.lambda(tb_train1)
tb_train_transformed <- BoxCox(tb_train1, lambda =lambda1)
tb_test_transformed <- BoxCox(tb_test1, lambda =lambda1)
Tb_transformed <- BoxCox(tb, lambda =lambda1)

#Plotting Transformed data 
autoplot(tb_train_transformed)
ggAcf(tb_train_transformed)
ggPacf(tb_train_transformed)

#Differencing to obtain stationarity
tb_train_diff_transformed=diff(tb_train_transformed)
tb_test_diff_transformed=diff(tb_test_transformed)
#Plotting Transformed and differenced data
autoplot(tb_train_diff_transformed)
ggAcf(tb_train_diff_transformed)
ggPacf(tb_train_diff_transformed)

#Testing order of differencing:
nsdiffs(tb_train_transformed)
#0
ndiffs(tb_train_transformed)
#1, confirming results of kpss test below

#KPSS test for stationarity
#install.packages("urca")
library(urca)
summary(ur.kpss(tb_train_diff_transformed))
ndiffs(tb_train_diff_transformed)
#0

```

###Basic Models###
```{r}

mean_tb<-meanf(tb_train_diff_transformed, h=22)
naive_tb<-naive(tb_train_diff_transformed, h=22)
snaive_tb<-snaive(tb_train_diff_transformed, h=22)
drift_tb<- rwf(tb_train_diff_transformed, drift=TRUE, h=22)
diff_tb_transformed <- diff(BoxCox(tb, lambda =lambda1))
length(diff_tb_transformed)
length(tb_train_diff_transformed)
tb.test<- window(diff_tb_transformed,  start=c(2018, 1))
plot(diff_tb_transformed, ylab = "Forecast of Differenced Rates", main = "Forecast Results from Simple Forecast Methods")
lines(mean_tb$mean, col = "red")
lines(naive_tb$mean, col = "blue")
lines(snaive_tb$mean, col = "yellow")
lines(drift_tb$mean, col = "green")
lines(tb.test,col = "orange")
legend("topright", legend = c("mean","naive","snaive","drift","true data"),
       col = c("red","blue","yellow","green","orange"),lty = 1:2,cex = 0.3) 
```

######ETS model#####
```{r}

object<-ets(tb_train_transformed)
library(forecast)
fit4<-forecast(object,
               h=22,
               level=c(80,95), fan=FALSE,
               simulate=FALSE, bootstrap=FALSE,
               npaths=5000, PI=TRUE,
               lambda=object$lambda, biasadj=FALSE)
autoplot(fit4, ylab = "Transformed T-Bill Rates")
# plot(tb_train_transformed,lwd=3,col="black")
# lines(object$state,lwd=1,col="red")
accuracy(fit4,tb_test_transformed)
summary(fit4)
#AIC     AICc      BIC 
#914.2691 914.3140 927.1326 
ets.aicc <- 914.3140
ets.aic <- 914.2691
ets.rmse <- 0.1948937
ets.mae <- 0.17693830
ets.mape <- 21.42893
ets.mase <- 0.4204676
checkresiduals(fit4)
#Ljung-Box test

#data:  Residuals from ETS(A,N,N)
#Q* = 135.5, df = 22, p-value < 2.2e-16

#Model df: 2.   Total lags used: 24

```
###### ARIMA #####
```{r}

#AUTO ARIMA
fit5 <- auto.arima(tb_train_transformed)
fit5 %>% forecast(h=22) %>% autoplot(include=538)
AIC(fit5)
# ARIMA(3,1,4)(1,0,1)[12] 
#[1] -913.0205

ggAcf(tb_train_transformed)
ggPacf(tb_test_transformed)
ggAcf(tb_train_diff_transformed)

# ARIMA LOOP ##
# aic_all = c()
# 
# for (i in 0:6){
#    for (j in 0:6){
#      for (m in 0:3){
#        for (n in 0:3){
#         fit=arima(tb_train_transformed,order = c(i,1,j),seasonal=c(m,0,n))
#          aic = fit$aic
#          aic_tmp = c(i,j,m,n,aic)
#          aic_all = rbind(aic_all,aic_tmp)
#        }
#      }
#    }
#  }
#  
#  z=which.min(aic_all[,5])
#  combos=cbind(1:784,aic_all)
#  combos[z,]

#this chooses an ARIMA(4,1,5) model
#AIC = -919.7687

fit6=arima(tb_train_transformed,order=c(4,1,5))
fit6 %>% forecast(h=22) %>% autoplot(include=538)
r.hat6<-predict(fit6,22)$pred
accuracy(r.hat6,tb_test_transformed)
AIC(fit6)
#[1] -919.7687
arima.aic <- AIC(fit6)
arima.rmse <- 0.1901198
arima.mae <- 0.1763157
arima.mape <- 21.70815



checkresiduals(fit6)

# Ljung-Box test
# 
# data:  Residuals from ARIMA(4,1,5)
# Q* = 28.349, df = 15, p-value = 0.01948
# 
# Model df: 9.   Total lags used: 24

```
###### GARCH model ######
```{r}
###### GARCH model ######

#fit the ARCH model
#install.packages("fGarch")
library(fGarch)
fit.arch = garchFit(~garch(1,0),data=tb_train_transformed,trace=F)
arch.mae<-mean(abs(fit.arch@residuals))
arch.mse<-mean((fit.arch@residuals)^2)
arch.mape<-mean(abs((fit.arch@residuals)/tb_train_transformed))*100
arch.rmse <- sqrt(mean((fit.arch@residuals)^2))

cbind(arch.mae,arch.rmse,arch.mape)
#    arch.mae arch.rmse arch.mape
#[1,] 1.148736  1.628596  240.1895
summary(fit.arch)
arch.aic <- 1.884714
#    AIC      BIC      SIC     HQIC 
#1.884714 1.909401 1.884647 1.894388 

#fit the GARCH model 
fit.garch = garchFit(~garch(1,1),data=tb_train_transformed,trace=F)
summary(fit.garch)
#AIC      BIC      SIC     HQIC 
#1.888563 1.921478 1.888444 1.901461 GARCH is unnecessary, the p-value for beta is 0.457
mae.garch<-mean(abs(fit.garch@residuals))
mse.garch<-mean((fit.garch@residuals)^2)
mape.garch<-mean(abs((fit.garch@residuals)/tb_train_transformed))*100
cbind(mae.garch,mse.garch,mape.garch)
# mae.garch mse.garch mape.garch
#[1,]  1.148765   2.65285   240.2336


# r.hat.garch<-predict(fit.garch,134)$pred
# accuracy(r.hat.garch,tb_test_transformed)

#Obtain standardized residuals
b=residuals(fit.arch,standardize=T)
plot(b,type='l')

#the residual plot show that it’s not a good fit
#To check adequacy, check both Ljung-Box of the residuals and the residuals squared
Box.test(b,10,type='Ljung')
#p-value is extremely small
#To check the adequacy of the mean equation
Box.test(b^2,10,type='Ljung')
#thus the ARCH model itself is far from enough though the ARCH effect exists


##GARCH LOOP
aic_all2 = c()

for (i in 1:4){
  for (j in 0:3){
    

        fit_garch_loop=garchFit(substitute(~ arma(4,5)+garch(p,q),list(p=i, q=j)),data=tb_train_diff_transformed,trace=F)
        
        aic2 = fit_garch_loop@fit$ics[1]
        aic_tmp2 = c(i,j,aic2)
        aic_all2 = rbind(aic_all2,aic_tmp2)

  }
}

z2=which.min(aic_all2[,3])
combos2=cbind(1:16,aic_all2)
combos2[z2,]
#                 i         j         AIC 
#2.000000  1.000000  1.000000 -2.077399 

#TEST
set.seed(777)
fit777=garchFit(~arma(4,5)+garch(1,1),data=tb_train_diff_transformed,trace=F)
summary(fit777)
# AIC       BIC       SIC      HQIC 
#-2.077399 -1.970265 -2.078632 -2.035413
mae.cob<-mean(abs(fit777@residuals))
mse.cob<-mean((fit777@residuals)^2)
mape.cob<-mean(abs((fit777@residuals)/tb_train_diff_transformed))*100
cbind(mae.cob,mse.cob,mape.cob)
#  mae.cob    mse.cob mape.cob
#[1,] 0.06922825 0.00970512      Inf

#test for Arch effect
fit777.residuals <- fit777@residuals
library(fpp2)
ggAcf(fit777.residuals)
pacf(fit777.residuals^2)
log(538)
#6.287859
#pred.garch1=predict(fit777,21)
#ARCH effect exists. Garch model can be used.

#forecast
#install.packages("rugarch")
library(rugarch)
library(fGarch)
spec <- ugarchspec(variance.model = list(model = "sGARCH", 
                                         garchOrder = c(1, 2), 
                                         submodel = NULL, 
                                         external.regressors = NULL, 
                                         variance.targeting = FALSE), 

                   mean.model     = list(armaOrder = c(4, 5), 
                                         external.regressors = NULL, 
                                         distribution.model = "norm", 
                                         start.pars = list(), 
                                         fixed.pars = list()))

garch <- ugarchfit(spec = spec, data = tb_train_diff_transformed, solver.control = list(trace=0))
pred.garch<-ugarchforecast(garch,n.ahead = 21)

pred.garch1<- ts(fitted(pred.garch), frequency=12, start=c(2018, 1))
pred.garch1
###Backtransforming GARCH 
final_value<- tb_train_transformed [length(tb_train_transformed)] 
pred.garch1[1] <- final_value+pred.garch1[1]
for (i in 2:22) { 
  pred.garch1[i] <- pred.garch1[i]+ pred.garch1[i-1]
  } 
plot.garch1<-plot(pred.garch1)
plot.garch1

plot(1:21, tb_test_diff_transformed,type='l',col='blue',lwd=2,xlim=c(1,21),xlab='Month',ylab = 'T-bill rates (transformed)')
lines( 1:21,fitted(pred.garch), type="o",pch=24, col="red",lwd=2) 
GARCH.mspe=mean((fitted(pred.garch)- tb_test_diff_transformed)^2) 
accuracy(fitted(pred.garch),tb_test_diff_transformed)
GARCH.mspe
#0.00523707
(fitted(pred.garch)
summary(fit777)
#AIC       BIC       SIC      HQIC 
#-2.077399 -1.970265 -2.078632 -2.035413 
garch.aic <- -2.077399
garch.rmse <- sqrt(mean((fitted(pred.garch)- tb_test_diff_transformed)^2))
garch.mape <-  100*(mean(abs((fitted(pred.garch)- tb_test_diff_transformed)/tb_test_diff_transformed)))
garch.mae <- mean(abs(fitted(pred.garch)- tb_test_diff_transformed))
#garch.mase <- mean(abs(fitted(pred.garch)-tb_test_transformed)/sum())
cbind(garch.mae,garch.rmse,garch.mape)
#    garch.mae garch.rmse garch.mape
#[1,]  0.052223 0.07237151  -33.38917
checkresiduals(fit777@residuals)
Box.test(fit777@fitted)
# Box-Pierce test
# 
# data:  fit777@fitted
# X-squared = 16.364, df = 1, p-value = 5.227e-05



```
#####SETAR MODEL##########
```{r}


#install.packages('tsDyn')
library(tsDyn)
fit8=linear(tb_train_transformed, m=1)#linear model
summary(fit8)
fit9= aar(tb_train_transformed, m=1) #non-linear additive AR model
summary(fit9)
Box.test(fit8$residuals,lag=10,type='Ljung')
Box.test(fit9$residuals,lag=10,type='Ljung')

AIC(fit8) #-2285.158
AIC(fit9) #-2269.158; linear model is better


fit.setar1<-setar(tb_train_transformed, m=2, thDelay=1)  
summary(fit.setar1)
AIC(fit.setar1) #-2374.759
acf(fit.setar1$residuals) #plot: project_setar1
Box.test(fit.setar1$residuals,lag=10,type='Ljung') # 3.835e-06
pred1=predict(fit.setar1,n.ahead=22)

mean((pred1-as.numeric(tb_test_transformed))^2) #MSE: 0.1812498
accuracy(pred1,tb_test_transformed)
# ME      RMSE       MAE      MPE     MAPE      ACF1 Theil's U
# Test set 0.3877714 0.4257344 0.3877714 43.21572 43.21572 0.7980753  5.051177
checkresiduals(fit.setar1)

fit.setar2 <- setar(tb_train_transformed, m=3, thDelay=1)
summary(fit.setar2)
AIC(fit.setar2) # -2394.382
acf(fit.setar2$residuals) #plot: project_setar2
Box.test(fit.setar2$residuals,lag=10,type='Ljung') #0.0004806
pred2=predict(fit.setar2,n.ahead=22)
mean((pred2-as.numeric(tb_test_transformed))^2) #MSE:  0.2749303


fit.setar4 <- setar(tb_train_transformed, m=4, thDelay=1)
summary(fit.setar4)
AIC(fit.setar4) #-2402.722
acf(fit.setar4$residuals) #plot: project_setar4
Box.test(fit.setar4$residuals,lag=10,type='Ljung') #0.01163
pred4=predict(fit.setar4,n.ahead=22)
mean((pred4-as.numeric(tb_test_transformed))^2) #MSE: 0.2237386

fit.setar5 <- setar(tb_train_transformed, m=5, thDelay=1)
summary(fit.setar5)
AIC(fit.setar5) #-2404.35, only improved by a slight amount. Selecting fit.setar4
acf(fit.setar5$residuals) #plot: project_setar4
Box.test(fit.setar5$residuals,lag=10,type='Ljung') # 0.00919
pred4=predict(fit.setar5,n.ahead=22)
mean((pred4-as.numeric(tb_test_transformed))^2) #MSE: 0.2558239

setar.aic <- -2402.722
setar.mae<-mean(abs(fit.setar4$residuals))
setar.rmse<-sqrt(mean((fit.setar4$residuals)^2))
setar.mape<-mean(abs((fit.setar4$residuals)/tb_train_transformed[1:516]))*100
c(setar.mae,setar.rmse,setar.mape)
#[1] 0.06464902 0.08821089 8.38877628

```
#########LSTAR MODEL#########
```{r}


fit.lstar <- lstar(tb_train_transformed, m=4, thDelay=1)
AIC(fit.lstar) #-2400.388
lstar.aic <- -2400.388
checkresiduals(fit.lstar$residuals)
pred.lstar <- predict(fit.lstar, n.ahead=22)
Box.test(fit.lstar$residuals,lag = 9, type = "Ljung")
#Box-Ljung test

#data:  fit.lstar$residuals
#X-squared = 21.408, df = 9, p-value = 0.01096
accuracy(pred.lstar, tb_test_transformed)
lstar.rmse <- 0.4782705
lstar.mae <- 0.4416052
lstar.mape <- 49.96487
plot(1:22,tb_test_transformed,type='l',col='black',lwd=2,xlim=c(1,22),xlab='Month',ylab = 't-bill rate')
lines( 1:22, pred.lstar, type="o",pch=24, col="red",lwd=2)


```
#########Neural Network Model#########
```{r}

set.seed(11)
fit.nn<-nnetar(tb_train_transformed)
summary(fit.nn)
pred.nn=forecast(fit.nn,22)
plot(1:22,tb_test_transformed,type='l',col='black',lwd=2,xlim=c(1,22),xlab='Month',ylab = 't-bill rate')
lines(1:22,pred.nn$mean, type="o",pch=24, col="red",lwd=2) 
accuracy(pred.nn,tb_test_transformed)
nn.rmse <- 0.72675805
nn.mae <- 0.53558385
nn.mape <- 0.53558385
nn.mase <- -73.245918
#  ME       RMSE        MAE        MPE      MAPE      MASE        ACF1 Theil's U
# Training set  0.0001973782 0.07235805 0.05513584  -3.910303  8.847313 0.1310221 -0.03272649        NA
# Test set     -0.5308377243 0.72675805 0.53558385 -73.245918 73.927265 1.2727354  0.86170642  11.39644

checkresiduals(fit.nn)
fit.nn%>%forecast(22)%>%autoplot()
Box.test(fit.nn$residuals,lag = 9, type='Ljung')
# Box-Ljung test
# 
# data:  fit.nn$residuals
# X-squared = 1.55, df = 9, p-value = 0.9968






```

####regression#####
```{r}

head(tb.rates)
unemployment <- ts(tb.rates$unemployment, frequency=12, start=c(1975, 1))
unemployment_train1 <- window(unemployment, end = c(2017,12))
unemployment_test1<-window(unemployment, start=c(2018, 1))
gdp <- ts(tb.rates$unemployment, frequency=12, start=c(1975, 1))
gdp_train1 <- window(gdp, end = c(2017,12))
gdp_test1<-window(gdp, start=c(2018, 1))
return <- ts(tb.rates$stock_return_nominal , frequency=12, start=c(1975, 1))
return_train1 <- window(return, end = c(2017,12))
return_test1<-window(return, start=c(2018, 1))
rr <- ts(tb.rates$stock_return_real , frequency=12, start=c(1975, 1))
rr_train1 <- window(rr, end = c(2017,12))
rr_test1<-window(rr, start=c(2018, 1))
cu <- ts(tb.rates$currency, frequency=12, start=c(1975, 1))
cu_train1 <- window(cu, end = c(2017,12))
cu_test1<-window(cu, start=c(2018, 1))
#install.packages("MASS")
library(MASS)
reg1 <- tslm(tb_train_transformed~unemployment_train1+return_train1+cu_train1+gdp_train1)
summary(reg1)
reg2 <- tslm(tb_train_transformed~unemployment_train1+return_train1+cu_train1)
summary(reg2)
AIC(reg2)
reg3<- tslm(tb_train_transformed~unemployment_train1)
AIC(reg3)
df <-data.frame(unemployment_test1,return_test1,cu_test1)
names <-c("unemployment_train1","return_train1","cu_train1")
colnames(df) <- names
fcast <- predict.lm(reg2, newdata =df,h=22)
plot(fcast)
summary(reg2)
checkresiduals(reg2)
#residuals are not white noise
accuracy(fcast,tb_test_transformed)
reg.aic <- 1059.271
reg.rmse <- 2.473038
reg.mae <- 2.464469
reg.mape <- 300.0599
#the model chosen is tb~unemployment+stock_return_nominal+currency
#gives unrealistic pred
```


#####prediction graph#####
```{r}
# ETS FIT4
#ARIMA r.hat6
# GARCH pred.garch$meanForecast
#setar pred4 
 #lstar pred.lstar
 #network pred.nn
plot(fcast)
par(mfrow=c(1,1))
plot(tb_test_transformed,col='black',xlab='time',ylab = '',ylim=c(0,2))
lines( r.hat6, type="l",pch=2, col="chocolate1")
lines(pred.garch1, type="l",pch=2, col="cyan4")
lines( pred4, type="l",pch=24, col="green",lwd = 0.5)
lines( pred.lstar, type="l",pch=24, col="blue",lwd=2)
lines( pred.nn$mean, type="l",pch=24, col="red",lwd=2)
legend('topleft',c('True', 'pred.ARIMA', 'pred.garch', 'pred.setar',
                  'pred.lstar','pred.nn'),lty=rep(1,5),
       col=c('black','chocolate1', 'cyan4','green','blue','red'),cex = 0.5)

```
cbind(ets.aic,arima.aic,garch.aic,setar.aic,lstar.aic,reg.aic)
#ets.aic arima.aic garch.aic setar.aic lstar.aic  reg.aic
#914.2691 -919.7686 -2.077399  -2404.35 -2400.388 1059.271

cbind(ets.mae,arima.mae,garch.mae,setar.mae,lstar.mae,reg.mae)
#ets.mae arima.mae garch.mae  setar.mae lstar.mae  reg.mae
#0.1769383 0.1763157 0.6039189 0.06464902 0.4416052 2.464469

cbind(ets.mape,arima.mape,garch.mape, setar.mape,lstar.mape,reg.mape)
#ets.mape arima.mape garch.mape  setar.mape lstar.mape reg.mape
#21.42893   21.70815   -33.38917  8.388776   49.96487 300.0599

cbind(ets.rmse,arima.rmse,setar.rmse,lstar.rmse,reg.rmse)
#ets.rmse arima.rmse garch.rmse setar.rmse lstar.rmse reg.rmse
#0.1948937  0.1901198 0.07237151  0.08821089  0.4782705 2.473038
